Why Donors Donate?

### 2020-09-09 analysis/05_market_simulator.Rmd
Added Sections for persona inputs in the beta_persona levels

beta_persona$levels = c("Intercept",
                        "Follow National News", 
                        "Follow International News",
                        "TV",
                        "Print",
                        "Online (excluding social media)",
                        "Social Media",
                        "Radio",
                        "Email",
                        "News app",
                        "Follow Government or Public Affairs", 
                        "Doesn't Travel", 
                        "Political Preference", 
                        "Trust in Political Institutions",
                        "Others Should be Charitable",
                        "Worship Service Attendence",
                        "Religious Importance",
                        "Protestant",
                        "Christian Orthodox",
                        "Jewish",
                        "Muslim",
                        "Sikh",
                        "Hindu",
                        "Buddhist",
                        "Atheist",
                        "Other (Religion)",
                        "Chartiy Trust Importance",
                        "Trust in Charity", 
                        "Donation Frequency", 
                        "Donation Amount",
                        "Not Volunteered",
                        "Volunteer Frequence",
                        "Personal Activism",
                        "Family Activism",
                        "Religious Membership", 
                        "Sport or Recreational Membership", 
                        "Art, Music, or Educational Membership",
                        "Labor Union Membership",
                        "Political Party Membership",
                        "Environmental Organization Membership",
                        "Professional Association", 
                        "Humanitarian or Charity Membership",
                        "Consumer Organization Membership",
                        "Other Organization Membership",
                        "Female",
                        "Transgender",
                        "Prefer not to say",
                        "Other (Gender)",
                        "Widowed",
                        "Divorced",
                        "Separated",
                        "Never Married",
                        "Education", 
                        "Income", 
                        "White", 
                        "Black", 
                        "American Indian", 
                        "Asian", 
                        "Pacific Islander", 
                        "Other (Race)", 
                        "Age")

>>>>

beta_persona$levels = c("Intercept",
                        # Follow National News
                        "Rarely", 
                        "Once a Week",
                        "At least once a day",
                        # Follow International News
                        "Never",
                        "Sometimes",
                        "Always",
                        # News Mediums
                        "TV",
                        "Print",
                        "Online (excluding social media)",
                        "Social Media",
                        "Radio",
                        "Email",
                        "News app",
                        # Follow Government or Public Affairs
                        "", 
                        # Travel to Countries
                        "Doesn't Travel", 
                        # Political Preference
                        "Political Preference", 
                        # Trust in Political Institute
                        "Trust in Political Institutions",
                        # Should Others be Charitable
                        "Others Should be Charitable",
                        # Worship Service Attendence
                        "Worship Service Attendence",
                        # Religious Importance
                        "Religious Importance",
                        # Religion
                        "Protestant",
                        "Christian Orthodox",
                        "Jewish",
                        "Muslim",
                        "Sikh",
                        "Hindu",
                        "Buddhist",
                        "Atheist",
                        "Other (Religion)",
                        # Charity Trust Importance
                        "Chartiy Trust Importance",
                        # Trust in Charities
                        "Trust in Charity", 
                        # Donation Frequency
                        "Donation Frequency", 
                        # Donation Amount
                        "Donation Amount",
                        # Volunteered last 12 months
                        "Not Volunteered",
                        # Volunteer Frequency
                        "Volunteer Frequency",
                        # Personal Activism
                        "Personal Activism",
                        # Family Activism
                        "Family Activism",
                        # Relgious Membership
                        "Religious Membership", 
                        # Sport or Recreational Membership
                        "Sport or Recreational Membership", 
                        # Art, Music, or Educational Membership
                        "Art, Music, or Educational Membership",
                        # Labor Union Membership
                        "Labor Union Membership",
                        # Political Party Membership
                        "Political Party Membership",
                        # Environmental Organization Membership
                        "Environmental Organization Membership",
                        # Professional Association
                        "Professional Association", 
                        # Humanitarian or Charity Membership
                        "Humanitarian or Charity Membership",
                        # Consumer Organization Membership
                        "Consumer Organization Membership",
                        #Other Organization Membership
                        "Other Organization Membership",
                        # Gender
                        "Female",
                        "Transgender",
                        "Prefer not to say",
                        "Other (Gender)",
                        # Marital Status
                        "Widowed",
                        "Divorced",
                        "Separated",
                        "Never Married",
                        # Education
                        "Education", 
                        # Income
                        "Income", 
                        # Race
                        "White", 
                        "Black", 
                        "American Indian", 
                        "Asian", 
                        "Pacific Islander", 
                        "Other (Race)", 
                        # Age
                        "Age")
